Numerical simulation of the Cordilleran ice sheet through the last glacial cycle

### 2014-05-15 cordillera-cycle.tex
Sketch paper outline.

@@

Figs.~\ref{fig:multirec-timeseries}, ~\ref{fig:multirec-snapshots},
~\ref{fig:hires-timeseries}, ~\ref{fig:hires-snapshots},
~\ref{fig:duration} and ~\ref{fig:deglac} about here.

@@

>>>>

\subsection{Ice thermodynamics}

\subsection{Bedrock response}

\subsection{Surface mass balance}

\subsection{Atmospheric forcing}

@@

\subsection{Palaeo-climate sensitivity test}

Figs.~\ref{fig:multirec-timeseries} and ~\ref{fig:multirec-snapshots}.

\subsection{High-resolution simulations}

Figs. ~\ref{fig:hires-timeseries} and ~\ref{fig:hires-snapshots},

@@

\subsection{Timing of glaciation}

\subsection{Extent of glaciation}

Fig~\ref{fig:duration} about here.

\subsection{Deglaciation patterns}

Fig ~\ref{fig:deglac} about here.
